---
title: "AirBnB Group Project"
author: "MFA - Stream A - Group 7"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(GGally)
library(readxl)
library(here)
library(skimr)
library(janitor)
library(broom)
library(vroom)
library(mosaic)
library(tidyquant)
library(infer)
library(openintro)
library(tidyquant)
library(leaflet)
library(broom)
library(car)
library(ggfortify)
library(kableExtra)
library(huxtable)
library(flextable)

```

```{r}
listings <- vroom("http://data.insideairbnb.com/turkey/marmara/istanbul/2020-06-28/data/listings.csv.gz")

listings <- listings %>%
  mutate(price = parse_number(price))

typeof(listings$price)

```

#Exploratory Data Analysis 
##What does the data set contain? 

```{r}
glimpse(listings)
skim(listings)
```

From our glimpse into the data frame, we see that there are 106 columns with a total of 23,728 rows. However of these 106 columns, skim() shows us that only 39 are of the type "numeric". These include variables such as "bedrooms", "square feet", "latitude" and "longitude". Investigating further, we see that a lot of the columns don't add anything of value in terms of analysis (e.g. id, listing_url, scrape_id) and will therefore be dropped later on. 

However, we also see that some of the columns you'd expect to be numeric (e.g. "price", "cleaning fee") are actually served as strings - we will therefore need to cast these for use in our analysis later on. 

##Categorical variables 
Checking for factor variables in our dataset, we first dive into the review section of hosts - surely AirBnB must have implemented a review system of 1-10? 

```{r}
listings %>%
  select(review_scores_value) %>%
  filter(review_scores_value != "NA") %>%
  group_by(review_scores_value) %>%
  count() %>% 
  ggplot(., aes(x = review_scores_value, y = n)) + geom_col()
```
Manipulating our dataframe to show the range of review scores, we see that AirBnB indeed has a 1-10 rating system, and judging from the scores given it seems that Istanbul has some great hosts! The reason why we don't see any 1 scores could perhaps be that AirBnB removes hosts who receive such a score very quickly. 

Other categorical values seem to be variables such as 
* maximum_nights (the max period you can rent an AirBnB is 365 days)
* zipcode (Istanbul has a finite amount of zipcodes)
* neighbourhood (Istanbul has a finite amount of neighbourhoods)

##Correlation between variables 
Before finding the correlation we need to clean the dataset, please refer to the next chapter (Cleaning the Dataset) to see how we did this. 
```{r}
ggpairs(listings_cleaned)
```
#Cleaning the dataset 
###Removing unneccesary variables
As we saw in our glimpse of the dataset, there are a few variables that have no relevancy, or at least cause a lot of noise when trying to manipulate the data. Let's remove some of the less important columns:
```{r}
#Keep relevant variables
listings_cleaned <- listings %>% 
  select(!c(id, scrape_id, last_scraped, experiences_offered, neighborhood_overview, thumbnail_url, thumbnail_url, medium_url, picture_url, xl_picture_url, host_id, host_url, host_name, host_location, host_about, host_thumbnail_url, host_picture_url, country, country_code, calendar_updated, has_availability, calendar_last_scraped, jurisdiction_names))

```
###Casting price 
Now let's turn the faulty character variables into the numerics they should be representing, starting with price 

```{r}

listings_cleaned <- listings_cleaned %>%
  mutate(price = parse_number(price))

typeof(listings_cleaned$price)

```
###Analyzing cleaning_fee 
Now, let's turn our focus to the cleaning_fee variable 

```{r}
#First we change it into a numerical variable

listings_cleaned <- listings_cleaned %>%
  mutate(cleaning_fee = parse_number(cleaning_fee))

skim(listings_cleaned$cleaning_fee)

```


We see that there's 13660 rows / ads missing a value for cleaning_fee. This most likely indicates that the ad **simply has no cleaning fee associated with renting the apartment**. 

Let's turn these missing values into zeroes, which more accurately convey what the dataset is trying to tell us: 

```{r}
listings_cleaned <- listings_cleaned %>%
  mutate(cleaning_fee = case_when(
    is.na(cleaning_fee) ~ 0, #Fill in a 0 when there is a N/A value
    TRUE ~ cleaning_fee
  ))

#Confirm there's no more missing values
skim(listings_cleaned$cleaning_fee)
#Confirmed!

```
###A deeper look into property_type 
Let's turn our attention to property_type. First we count how many categories make up the variable's frequency 

```{r}
property_count <- listings_cleaned %>%
  group_by(property_type) %>%
  count() %>%
  arrange(desc(n))

property_count

```
We see that the top 4 most common property types are:

1. Apartment
2. Serviced apartment
3. House
4. Boutique hotel 

These four make up...

```{r}
totalproperty_count <- listings_cleaned %>%
  select(property_type) %>%
  count() #Count total properties in the dataset

property_count %>%
  head(4) %>% #Choose the top 4 (apt, serviced apt, house, boutique)
  arrange(desc(n)) %>%
  ungroup() %>% #Prime for summarization  
  summarise(sum4 = sum(n)) %>% #Get sum of the top 4 property type
  mutate(proportion4 = sum4/totalproperty_count$n) #Calculate the proportion 

```

A whole **81.5%** as seen from the data manipulation above. Let's now create a simplified version of the property_type variable with 5 categories: 

* Apartment
* Serviced Apartment
* House
* Boutique Hotel 
* Other 

```{r}
listings_cleaned <- listings_cleaned %>%
  mutate(prop_type_simplified = case_when(
    property_type %in% c(
      "Apartment",
      "Serviced apartment", 
      "House",
      "Boutique hotel") ~ property_type, #When the property type matches one of these four, keep the value  
    TRUE ~ "Other" #Otherwise turn it into "Other" 
  ))

#Checking that our code is correct 
listings_cleaned %>%
  count(property_type, prop_type_simplified) %>%
  arrange(desc(n))  

#Checks out! 
```
###minimum_nights and filtering away non-travellers
Let's now turn our attention to the minimum_nights variable 

```{r}
listings_cleaned %>% 
  group_by(minimum_nights) %>%
  count() %>%
  arrange(desc(n))

```
The most common values (top 5) are: 

1. 1 night 
2. 2 nights 
3. 3 nights 
4. 7 nights 
5. 5 nights 

Plotting this as a ggplot would result in a very ugly diagram. We see that using AirBnB to stay for 1 night in Istanbul seems very popular representing more than 60% of the top 5 booking durations. 

There could be several reasons why this is the case, but our hypothesis is that: 

* Tourists jump from one AirBnB to the next as they explore various parts of this vibrant, cultural city e.g. living near the Blue Mosque one day, moving to Taksim Square the next before crossing the Bosphorous Strait into the Asian part of Istanbul. 

We will now filter the minimum_nights so that only observations <= 4 are included in the dataset 

```{r}
listings_cleaned <- listings_cleaned %>%
  filter(minimum_nights <= 4)

```

#Mapping 

```{r}
leaflet(data = filter(listings_cleaned, minimum_nights <= 4)) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1, 
                   fillColor = "blue", 
                   fillOpacity = 0.4, 
                   popup = ~listing_url,
                   label = ~property_type)

```

#Regression Analysis

```{r}
listings_cleaned <- listings_cleaned %>%
  mutate(extra_people = parse_number(extra_people))

```

```{r}
max(listings_cleaned$price)
total_cost_1 <- listings_cleaned %>%
  filter(guests_included == 1) %>%
  mutate(cost = (4 * price + 4 * extra_people + cleaning_fee))

total_cost_2 <- listings_cleaned %>%
  filter(guests_included >= 2) %>%
  mutate(cost = (4 * price + cleaning_fee))

listings_cleaned <- full_join(total_cost_1, total_cost_2, copy = FALSE)

listings_cleaned <- listings_cleaned %>%
  mutate(price_4_nights = cost)

options("scipen"=100, "digits"=4)

ggplot(listings_cleaned, aes(x=price_4_nights)) + geom_histogram() + labs(title = "Price of staying at an Airbnb location for 4 nights", x = "Costs of 4-night stays", y = "No. of couples")

ggplot(listings_cleaned, aes(x=price_4_nights)) + geom_histogram() + scale_x_log10() +labs(title = "Price of staying at an Airbnb location for 4 nights", x = "Costs of 4-night stays", y = "No. of couples") 

```

For the regression model we would think of the following explanatory variables:

* Neighborhood 
* Bedrooms
* Accomodates 
* Square feet 
* Property type 

These are based on our own experience when we're looking for places to stay. We have found that the above variables usually play a big part in determining the price of the listing. 

```{r}
model1 <- lm(price_4_nights ~ number_of_reviews + prop_type_simplified + review_scores_rating, data = listings_cleaned)

summary(model1)
#According to model1, if the review score rating of an Airbnb location rises by 1, the price of a couple staying at that location for 4 nights would decrease by 10.77.

#According to model1, an increase in the number of boutique hotels by 1 would raise the cost of a 4-night stay for a couple by 452.91. An equivalent increase for serviced apartments would raise the cost by 439.45. Houses are the only type of property which have a negative relationship with price, decreasing the cost by 21.03 for each additional house. All other property types such as apartments, townhouses, condominiums, aparthotels, bed and breakfasts, and lofts, have counts positively correlated with the cost of a 4-night stay for a couple.

model2 <- lm(price_4_nights ~ number_of_reviews + room_type + prop_type_simplified + review_scores_rating, data = listings_cleaned)
summary(model2)

#From this new regression model, we see an increase in the adjusted R^2 value meaning that room_type indeed seems to be a predictor of the cost for 4 nights. This is also seen by the t-values of the various room types - everyone of them is significant.   

```


#Further variables/question to explore
 
In this part, we will further investigate the relationship between several variables to extend our analysis. First, an overview of the relationship we investigate will be given. Then, the relationship will be investigated, and finally, a written conclusion will be presented.

##Can we use the number of bathrooms, bedrooms, beds and the size of the house to predict the price of a four night stay?

To start, we will investigate whether the number of bathrooms, bedrooms, beds or the size of the house are significant predictors of the price for a four night stay as it was calculated in the previous chapter. 
```{r}
mymodela <- lm(price_4_nights ~ bathrooms, data = listings_cleaned)
msummary(mymodela)
```
The t value of 10.9 tells us that the number of bathrooms is a significant predictor of the price for four nights. Our model estimates every bathroom adds about 556.1$ to the price of a four nights stay.
```{r}
mymodelb <- lm(price_4_nights ~ bedrooms, data = listings_cleaned)
msummary(mymodelb)
```
The t value of 10.0 tells us that the number of bedrooms is a significant predictor of the price for four nights. Our model estimates every bedroom adds about 371.4$ to the price of a four nights stay.
```{r}
mymodelc <- lm(price_4_nights ~ beds, data = listings_cleaned)
msummary(mymodelc)
```
The t value of 12.6 tells us that the number of beds is a significant predictor of the price for four nights. Our model estimates every bed adds about 326.7$ to the price of a four nights stay.
```{r}
mymodeld <- lm(price_4_nights ~ accommodates, data = listings_cleaned)
msummary(mymodeld)
```
The t value of 19.79 tells us that the amount of people an AirBnB can accommodate is a significant predictor of the price for four nights. Our model estimates every person an apartment can accommodate adds about 481.7$ to the price of a four nights stay.
```{r}
mymodele <- lm(price_4_nights ~ bathrooms + bedrooms + beds + accommodates, data = listings_cleaned)
msummary(mymodele)
```
When running our model for all the variables at the same time. At first sight, we find that the amount of beds is not a significant predictor anymore and that extra bedrooms actually decrease the price of the four night stay. It is important to note that our multi-collinearity test works best when there is zero correlation between the explanatory variables. No test is needed to see that this is not the case in our example, the amount of people an apartment can accommodate and the number of bedrooms is obviously correlated to the number of beds and so is the amount of bathrooms. It is for this reason that we cannot draw conclusions from the above linear model without making appropriate adaptations. 

##Do superhosts command a pricing premium?

Now, lets investigate whether superhosts command a pricing premium after controlling for other variables. 
The way we would control for other (confounding) variables is to include them in our regression model and see if the variable we want to investigate is still a significant predictor. The problem is we will never know if we have taken care of all the variables that we need to (which is called residual confounding) but we try our best to get an answer that is as close to correct as possible. 

Lets first look at which variables are available in our cleaned dataset:
```{r}
glimpse(listings_cleaned)
skim(listings_cleaned)
```

We assume that controlling for all other variables that characterise the host will allow us to single out the effect of being a superhost (or not being-). 

First, lets create a new variable so that we can adjust for the number of host verifications:
```{r}
listings_cleaned_f <- listings_cleaned %>%
  mutate(number_of_verifications = length(host_verifications))
```

Now, we use the following linear model:
```{r}
mymodelf <- lm(price ~ host_is_superhost + host_total_listings_count + host_has_profile_pic + host_identity_verified + number_of_verifications, data = listings_cleaned_f)
msummary(mymodelf)
```
As you can see, we did not take the response time, response rate or neighbourhood of the host into account since these variables are only known for a very limited amount of hosts. 
We find that the superhosts command a price premium as this is a significant predictor even after controlling for the previously mentionned variables. We observe that in the fact that it has a t value of 2.2 and a Pr(>|t|) of 0.0277. Do note that this model only explains a very small part of the price as we see that Adjusted R-squared is only 0.0529.

##Can the fact that a listing has an exact location be used to predict the price of a four night stay?

Lets investigate whether the fact that a property has or has not listed its exact location is a significant predictor of the price of our four night stay. Using a similar strategy as above, we first looked at the available variables. We suspect we will have to control for the effect of a listing being complete in its information in general so that we will find the effect of specificly having the exact location available.
In the following code, we create a variable that is 0 is no summary is available and 1 if a summary is available. We do the same thing for space, description, notes, transit, access and interaction.  
```{r}
listings_cleaned_g <- listings_cleaned %>%
mutate(summary_available = ifelse(is.na(summary), 0, 1), 
       space_available = ifelse(is.na(space), 0, 1),
       description_available = ifelse(is.na(description), 0, 1),
       notes_available = ifelse(is.na(notes), 0, 1),
       transit_available = ifelse(is.na(transit), 0, 1),
       access_available = ifelse(is.na(access), 0, 1),
       interaction_available = ifelse(is.na(interaction), 0, 1))
glimpse(listings_cleaned_g)
```

After glancing at our new variables, we see that there is a very strong correlation between them but this should not be a problem when we only want to test for the significance of the exact location and use these variables to control for other factors. 

```{r}
mymodelg <- lm(price_4_nights ~ is_location_exact + summary_available + description_available + notes_available + transit_available + access_available + interaction_available, data=listings_cleaned_g)
msummary(mymodelg)
```

We conclude that the availabliity of an exact locatyion of the listing is a significant predictor for the price of our 4 night stay since the t value is 4.19. Again, do note that this model only explains a very small part of the price as we see that Adjusted R-squared is only 0.00248.

##Is location a predictor of the price of our four night stay? 

For this question, we will start by grouping the neighbourhoods to divide them into 6 geographical areas: Center (C), North (N), East (E), Far East (FE), West (W), Far West (FW).
```{r}
listings_cleaned_g <- listings_cleaned %>%
  mutate(neighbourhood_simplified = case_when(neighbourhood_cleansed == "Atasehir" ~ "East",
                                              neighbourhood_cleansed == "Bagcilar" ~ "West",
                                              neighbourhood_cleansed == "Bakirkoy" ~ "West",
                                              neighbourhood_cleansed == "Bayrampasa" ~ "West",
                                              neighbourhood_cleansed == "Beykoz" ~ "North",
                                              neighbourhood_cleansed == "Beyoglu" ~ "Center",
                                              neighbourhood_cleansed == "Catalca" ~ "Far West",
                                              neighbourhood_cleansed == "Esenler" ~ "West",
                                              neighbourhood_cleansed == "Eyup" ~ "North",
                                              neighbourhood_cleansed == "Gaziosmanpasa"~ "West",
                                              neighbourhood_cleansed == "Kadikoy" ~ "East",
                                              neighbourhood_cleansed == "Kartal" ~ "Far East",
                                              neighbourhood_cleansed == "Maltepe" ~ "East",
                                              neighbourhood_cleansed == "Sancaktepe" ~ "Far East",
                                              neighbourhood_cleansed == "Sile" ~ "Far East",
                                              neighbourhood_cleansed == "Sisli" ~ "Center",
                                              neighbourhood_cleansed == "Sultangazi" ~ "Far West",
                                              neighbourhood_cleansed == "Umraniye" ~ "East",
                                              neighbourhood_cleansed == "Zeytinburnu" ~ "West",
                                              neighbourhood_cleansed == "Arnavutkoy" ~ "North",
                                              neighbourhood_cleansed == "Avcilar" ~ "Far West",
                                              neighbourhood_cleansed == "Bahcelievler" ~ "West",
                                              neighbourhood_cleansed == "Basaksehir" ~ "Far West",
                                              neighbourhood_cleansed == "Besiktas" ~ "Center",
                                              neighbourhood_cleansed == "Beylikduzu" ~ "Far West",
                                              neighbourhood_cleansed == "Buyukcekmece" ~ "Far West",
                                              neighbourhood_cleansed == "Cekmekoy" ~ "Far East",
                                              neighbourhood_cleansed == "Esenyurt" ~ "Far West",
                                              neighbourhood_cleansed == "Fatih" ~ "Center",
                                              neighbourhood_cleansed == "Gungoren" ~ "West",
                                              neighbourhood_cleansed == "Kagithane" ~ "North",
                                              neighbourhood_cleansed == "Kucukcekmece" ~ "Far West",
                                              neighbourhood_cleansed == "Pendik" ~ "Far East",
                                              neighbourhood_cleansed == "Sariyer" ~ "North",
                                              neighbourhood_cleansed == "Silivri" ~ "Far West",
                                              neighbourhood_cleansed == "Sultanbeyli" ~ "Far East",
                                              neighbourhood_cleansed == "Tuzla" ~ "Far East",
                                              neighbourhood_cleansed == "Uskudar" ~ "Center")) 
```

Now, lets create a model that will show us whether the areas we just created are significant predictors of the price of the four night stay. 
```{r}
mymodelg <- lm(price_4_nights ~ neighbourhood_simplified, data = listings_cleaned_g)
msummary(mymodelg)
```

We observe a p-value for our model of 4.63e-12. This means that the area to which a property belongs is indeed a significant predictor of the price of our four night stay. As we suspected, the properties in the center of the city are the most expensive for us to stay at for four nights.

##What is the effect of the cancellation policy on the price of our four night stay?

For this question, we will investigate whether the cancellation policy has an effect on the price of our four night stay. Using a similar strategy as for the previous questions, we first looked at the available variables.

```{r}

mymodeli <- lm(price_4_nights ~ cancellation_policy + bedrooms +  bathrooms + accommodates, data = listings_cleaned)
summary(mymodeli)
```
We see that cancellation_policy indeed is a strong explanatory variable for the price for a 4-night stay in Istanbul. We see that the cancellation policy of a listing negatively affects the price for four nights. If a listing has a moderate cancellation policy, the price for four nights is lowered by $307 

If a listing has a strict policy with a 14 days grace period, the listing price is lowered by $342 

##Diagnostics, collinearity, summary tables 
###Checking residuals of all the models 
```{r}
autoplot(model1)
autoplot(model2)
autoplot(mymodela)
autoplot(mymodelb)
autoplot(mymodelc)
autoplot(mymodeld)
autoplot(mymodele)
autoplot(mymodelf)
autoplot(mymodelg)
autoplot(mymodeli)







```

###Finding the Variance Inflation Factor 
####Model 1 
```{r}
vif(model1)
```
Model 1 looks OK regarding VIF-scores. 

####Model 2 
```{r}
vif(model2)
```
Model 2 looks OK regarding VIF-scores. 

####Model A - D
Only one explanatory variable for these models hence no need to check for multicollinearity. 

####Model E
```{r}
vif(mymodele)
```

Again a rather low VIF-score across the board.

####Model F
```{r}
vif(mymodelf)
```
VIF throws an error here saying there's atleast one aliased coefficient in the model, meaning that they share a perfect multicollinearity. Let's find out which ones those are: 

```{r}
alias(mymodelf) 
```
It seems that number_of_verifications is our culprit, let's run the regression without it. 

```{r}
modelf_adjusted <- lm(price ~ host_is_superhost + host_total_listings_count + host_has_profile_pic + host_identity_verified, data = listings_cleaned_f)

vif(modelf_adjusted)
```
This seem to have solved the problem, now let's see if our regression tells us something novel. 

```{r}
summary(modelf_adjusted)
```
We still find that there indeed is a price premium if a host is a super-host. Furthermore, we also still see that the total listings count have an impact on the price (premium). R-squared is still 0.0529, so removing the variable did not improve our model.

####Model G
Fewer than 2 terms so no use in VIF 

####Model I 
```{r}
vif(mymodeli)
```
No problems here either. 

###Summary Tables (huxtable)
```{r}
huxreg(list(
  "Model 1" = model1, 
  "Model 2" = model2, 
  "Model A" = mymodela, 
  "Model B" = mymodelb, 
  "Model C" = mymodelc, 
  "Model D" = mymodeld, 
  "Model E" = mymodele, 
  "Model F" = modelf_adjusted, 
  "Model G" = mymodelg, 
  "Model I" = mymodeli), statistics = c
       ('#observations' = 'nobs', 
        'R squared' = 'r.squared', 
        'Adj. R Squared' = 'adj.r.squared', 
        'Residual SE' = 'sigma'), 
bold_signif = 0.05
)
```

###Our best model 
Looking at our huxtable, we see that Model F seems to have the best explanatory power for staying at an AirBnB for four nights in Istanbul. However, it's important to note that **all of our models have a very poor prediction power...**

```{r}
tidy(modelf_adjusted)
```
```{r}
glance(modelf_adjusted)
```
That is: 

```{r}
prediction_model <- 700.189+95.675*(host_is_superhostTRUE)+1.895*(host_total_listings_count)-274.105*(host_has_profile_picTRUE)-48.655*(host_identity_verifiedTRUE)
```
Following the filter criteria set forth in the problem, we predict the cost: 

```{r}
final_prediction <- listings_cleaned %>%
filter(prop_type_simplified == "Apartment", room_type == "Private room", number_of_reviews >= 10, review_scores_rating > 90)  %>%
  group_by(listing_url) %>%
  mutate(host_is_superhost = case_when(host_is_superhost == TRUE ~ 95.675,
                                       host_is_superhost == FALSE ~ 0)) %>%
  mutate(host_total_listings_count = case_when(host_total_listings_count > 0 ~ count(host_total_listings_count) * 1.84,
                                               host_total_listings_count == 0 ~ 0)) %>%
  mutate(host_has_profile_pic = case_when(host_has_profile_pic == TRUE ~ -478.568,
                                          host_has_profile_pic == FALSE ~ 0)) %>%
  mutate(host_identity_verified = case_when(host_identity_verified == TRUE ~ -48.655,
                                            host_identity_verified == FALSE ~ 0)) %>%
  summarise(predicted_cost = sum(700.189 + host_is_superhost + host_total_listings_count + host_has_profile_pic + host_identity_verified))
```

We see that the total cost of staying at an AirBnB in Istanbul for four days fitting the criteria set forth above varies from: 
* Lowest price: 377.4 (found using slice())
* Highest price: 523.7

From our regression model we know that there is a standard error for every explanatory variable. Let's find the 95% confidence interval for the above prices: 

```{r}
LOWER_final_prediction <- listings_cleaned %>%
filter(prop_type_simplified == "Apartment", room_type == "Private room", number_of_reviews >= 10, review_scores_rating > 90)  %>%
  group_by(listing_url) %>%
  mutate(host_is_superhost = case_when(host_is_superhost == TRUE ~ 52.215, #Minus the standard error for every variable 
                                       host_is_superhost == FALSE ~ 0)) %>%
  mutate(host_total_listings_count = case_when(host_total_listings_count > 0 ~ count(host_total_listings_count) * 1.895,
                                               host_total_listings_count == 0 ~ 0)) %>%
  mutate(host_has_profile_pic = case_when(host_has_profile_pic == TRUE ~ -274.105,
                                          host_has_profile_pic == FALSE ~ 0)) %>%
  mutate(host_identity_verified = case_when(host_identity_verified == TRUE ~ -85.278,
                                            host_identity_verified == FALSE ~ 0)) %>%
  summarise(LOWER_predicted_cost = sum(496.227 + host_is_superhost + host_total_listings_count + host_has_profile_pic + host_identity_verified)) 
```

```{r}
HIGHER_final_prediction <- listings_cleaned %>%
filter(prop_type_simplified == "Apartment", room_type == "Private room", number_of_reviews >= 10, review_scores_rating > 90)  %>%
  group_by(listing_url) %>%
  mutate(host_is_superhost = case_when(host_is_superhost == TRUE ~ 139.135,
                                       host_is_superhost == FALSE ~ 0)) %>%
  mutate(host_total_listings_count = case_when(host_total_listings_count > 0 ~ count(host_total_listings_count) * 1.95,
                                               host_total_listings_count == 0 ~ 0)) %>%
  mutate(host_has_profile_pic = case_when(host_has_profile_pic == TRUE ~ -69.642,
                                          host_has_profile_pic == FALSE ~ 0)) %>%
  mutate(host_identity_verified = case_when(host_identity_verified == TRUE ~ -12.032,
                                            host_identity_verified == FALSE ~ 0)) %>%
  summarise(predicted_cost = sum(904.151 + host_is_superhost + host_total_listings_count + host_has_profile_pic + host_identity_verified))
```
To conclude, we therefore see that:

####Predicted Price (Point)
* Lowest price: 377.4 (found using slice())
* Highest price: 523.7

####Intervals 
For our minimum and maximum price we see that the confidence interval set gives us: 
* minimum price with 95% confidence = 136.8 to 822.5
* maximum price with 95% confidence = 276.2 to 975.6

The wide price range tells us that our model is poor at predicting the price. However, this model F had the highest R-squared value out of the possible models. 
